\documentclass[7pt,a4paper]{moderncv}

\usepackage{fullpage}
\usepackage[english]{babel}
\usepackage[scale=0.8]{geometry}


\moderncvtheme[blue]{classic} 
\newenvironment{tightitemize}
   {\begin{itemize}
   \setlength{\parskip}{2pt}}
   {\end{itemize}}

\linespread{0.9}

\firstname{Tristian Paul}
\familyname{Lopez Azuara}
\address{San Diego, CA}{Palm Avenue 1600 \#11, 92154}
\mobile{(619) 400-3392}

\email{tristian.azuara@gmail.com}
\title{Full Web Stack Developer}

\begin{document}
\vspace*{-22mm}
{\Huge Tr\'istian Pa\'ul L\'opez Azuara} \hfill Full Web-stack Developer
\vspace*{-8mm}
\begin{center}
\line(1,0){500}
\end{center}
\vspace*{-3mm}
\begin{tabular}{l c r}
{\Large\Phone} {\small (619) 400-3392}  & 
{\Large\Writinghand} {\small San Diego, CA. Palm Avenue 1600 \#11, 92154} \hfill  & 
{\Large\Letter} \href{mailto:tristian.azuara@gmail.com}{tristian.azuara@gmail.com}
\end{tabular}

\vspace*{-3mm}
\section{Employment - 4.5 Years}

\subsection{Software Developer -- Progreso Financiero (Contractor)  (2013 -- Current -- 11 Months)}
\cvitem{\textbf{Front-end Developer}}{
	Develop features and implement bug fixes for web application that allowed customers to apply for loans.
}

\subsection{Software Developer -- Core Covers  (2010 -- 2013)}

\cvitem{\textbf{Web Developer}}{
  Developed 3 Web Applications (Front-end and Back-end). Applications were used by customers and employees.
  Such applications \emph{held customer service costs at minimum} by having a streamlined and efective user experience.
}

\cvitem{\textbf{Information Architect}}{
	Organize, collect and categorize the information across departments.
	Proposed and implemented systems that managed and consumed such information.
	Automated and reduced cost of manufacturing operations eliminating duplicated 
	information.
}

\cvitem{\textbf{Database Administrator}}{
  Designed and maintained relational databases. 
  Cleaned and restored integrity of data.	  
  Optimized and normalized (3NF) the databases.
}

\cvitem{\textbf{Server Administrator}}{ 
  Installed, configured and managed private DNS, Web, Database servers and LAN shares.
}

\vspace*{-8mm}
\section{Skills}{
\cvitem{Languages}{English: Fluent, Spanish: First language}
\cvdoubleitem{Front-end Development}{{\flushleft 4 Years: \emph{Javascript (jQuery)}, HTML, CSS \\ 1 Year: Backbone, LESS, Underscore, Bootstrap \\ 6 Months: Zurb Foundation, Handlebars.js}
}
{Back-end Development}{\flushleft 4 Years: Java (Tomcat 7, Servlets, Jersey (JAX-RS)) \\ 3 Years: PHP \\ 2.5 Years: Python (Tryton ERP, Django) \\ 6 Months: C#}
\cvdoubleitem{Infrastructure}{Nginx, MySQL, PostgreSQL, Bind9, MoinMoin, }
				{Toolchain}{UNIX Based OS, Git, Vagrant, VirtualEnv, Simple Makefiles, Bash}
\\
\section{Relevant Projects}
\vspace*{-10mm}
\begin{tightitemize}

\item\textbf{(Progreso Financiero) Single-Page Application: }{Javascript, Backbone.js, Underscore.js, LESS, Bootstrap}
	Application allowed for customers to request responsible loans; the company's flagship product. Implemented new features,
	improved existing ones where adequate. A Scrum based development style was used. 

\item \textbf{(Core Covers) Web Application: }{PHP, Javascript, jQuery, CSS, HTML, MySQL:}
	Order fulfillment web application. Used as a customer onboarding offering, used by 50+ customers in
	a manufacturing environment. End users were company customers and customer service representatives; the 
	application was designed to maximize employee output and minimize customer effort, keeping both parties
	satisfied.
	
\item\textbf{(Core Covers) Web Application}{Java Servlets, HTML, JSON:}
	A web service API that exposed information contained in the local manufacturing system.
	It queried an MS Access database using a custom built C\# client; the API produced output
	in the JSON format.

\item \textbf{(UABC) Static Site Application: }{Javascript, Handlebars.js}
	Front-end part of a web application that eased the assessment and analysis of the Minnesota Multiphasic Personality Inventory 2 (MMPI-2) test.
	The application allowed the clinician to search for particular personality profiles, by applicant name, gender or other search parameters.
	Data was obtained from a JSON API. It was implemented as multimple pages that used Javascript to render.

\item \textbf{(UABC) Web API: }{Java JAX-RS, MySQL, Jetty 9.x:}
	Back-end part of a web application that assessed and allowed for querying of the MMPI-2 test results. It calculated the test key using
	Raw, T-Linear and T-Normalized scores. It exposed data as a JSON api implemented with the Java Jersey (JAX-RS) framework and with MySQL as
	the persistance engine.


\end{tightitemize}
\vspace*{-5mm}
\section{Education}
\cventry{2008  -- Present}{Computer Engineering}{Universidad Autonoma de Baja California}{Tijuana}{}{
	Software Engineering; Algorithms; Object Oriented Programming; Interaction Design; Artificial Intelligence; Computer Architecture; Technical Documentation; Analysis and Design of Systems;
	CUDA Development (Parallel Programming) ;Databases; Operating Systems (Architecture and elements);
} 
\cventry{2005 -- 2008}{Computer Technician}{Centro de Estudios Tecnol\'ogicos Industrial y de Servicios N\'umero 58}{Tijuana}{}{}

\end{document}